Advanced case study options

### 2018-05-14 notebook/ms/SI4.Rmd
Vignette made, need SI too

```{r}
for(ID in 2:9){
    cells_owned            <- sum(sim_old$LAND[,,3] == ID);
    sim_old$AGENTS[ID, 17] <- 100 * cells_owned;
}
```

@@

```{r, echo = TRUE, eval = TRUE}
# First initialise a simulation
sim_old  <- gmse_apply(get_res = "Full", remove_pr = 0.122, lambda = 0.275,
                       res_death_K = 93870, RESOURCE_ini = 35000, 
                       manage_target = 70000, res_death_type = 3,
                       manager_budget = 10000, user_budget = 10000,
                       public_land = 0.4, stakeholders = 8, res_consume = 0.02, 
                       res_birth_K = 200000, land_ownership = TRUE,
                       observe_type = 3, agent_view = 1, converge_crit = 0.01,
                       ga_mingen = 200, res_move_type = 0);
# By setting `res_move_type = 0`, no resource movement will occur in gmse_apply
# Adjust the landscape ownership below
sim_old$LAND[1:20,   1:20,  3] <- 2; 
sim_old$LAND[1:20,  21:40,  3] <- 3;
sim_old$LAND[1:20,  41:60,  3] <- 4;
sim_old$LAND[1:20,  61:80,  3] <- 5;
sim_old$LAND[1:20,  81:100, 3] <- 6;
sim_old$LAND[21:40,  1:50,  3] <- 7;
sim_old$LAND[21:40, 51:100, 3] <- 8;
sim_old$LAND[41:60,  1:100, 3] <- 9;
sim_old$LAND[61:100, 1:100, 3] <- 1;
# Change the budgets of each farmer based on the land they own
for(ID in 2:9){
    cells_owned            <- sum(sim_old$LAND[,,3] == ID);
    sim_old$AGENTS[ID, 17] <- 100 * cells_owned;
}
# Begin simulating time steps for the system
sim_sum_2 <- matrix(data = NA, nrow = 30, ncol = 5);
for(time_step in 1:30){
    # Apply the new movement rules at the beginning of the loop
    sim_old$resource_array  <- avoid_aggregation(sim_old$resource_array);
    # Next, move on to simulate (old_list remembers that res_move_type = 0)
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    sim_sum_2[time_step, 1] <- time_step;
    sim_sum_2[time_step, 2] <- sim_new$basic_output$resource_results[1];
    sim_sum_2[time_step, 3] <- sim_new$basic_output$observation_results[1];
    sim_sum_2[time_step, 4] <- sim_new$basic_output$manager_results[3];
    sim_sum_2[time_step, 5] <- sum(sim_new$basic_output$user_results[,3]);
    sim_old                 <- sim_new;
}
colnames(sim_sum_2) <- c("Time", "Pop_size", "Pop_est", "Cull_cost", 
                         "Cull_count");
print(sim_sum_2);
```

>>>>

```{r}
for(ID in 2:9){
    cells_owned            <- sum(sim_old$LAND[,,3] == ID);
    sim_old$AGENTS[ID, 17] <- 10 * cells_owned;
}
```

@@

```{r, echo = TRUE, eval = TRUE}
# First initialise a simulation
sim_old  <- gmse_apply(get_res = "Full", remove_pr = 0.122, lambda = 0.275,
                       res_death_K = 93870, RESOURCE_ini = 35000, 
                       manage_target = 70000, res_death_type = 3,
                       manager_budget = 10000, user_budget = 10000,
                       public_land = 0.4, stakeholders = 8, res_consume = 0.02, 
                       res_birth_K = 200000, land_ownership = TRUE,
                       observe_type = 3, agent_view = 1, converge_crit = 0.01,
                       ga_mingen = 200, res_move_type = 0);
# By setting `res_move_type = 0`, no resource movement will occur in gmse_apply
# Adjust the landscape ownership below
sim_old$LAND[1:20,   1:20,  3] <- 2; 
sim_old$LAND[1:20,  21:40,  3] <- 3;
sim_old$LAND[1:20,  41:60,  3] <- 4;
sim_old$LAND[1:20,  61:80,  3] <- 5;
sim_old$LAND[1:20,  81:100, 3] <- 6;
sim_old$LAND[21:40,  1:50,  3] <- 7;
sim_old$LAND[21:40, 51:100, 3] <- 8;
sim_old$LAND[41:60,  1:100, 3] <- 9;
sim_old$LAND[61:100, 1:100, 3] <- 1;
# Change the budgets of each farmer based on the land they own
for(ID in 2:9){
    cells_owned            <- sum(sim_old$LAND[,,3] == ID);
    sim_old$AGENTS[ID, 17] <- 10 * cells_owned;
}
# Begin simulating time steps for the system
sim_sum_2 <- matrix(data = NA, nrow = 30, ncol = 5);
for(time_step in 1:30){
    # Apply the new movement rules at the beginning of the loop
    sim_old$resource_array  <- avoid_aggregation(sim_old$resource_array);
    # Next, move on to simulate (old_list remembers that res_move_type = 0)
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    sim_sum_2[time_step, 1] <- time_step;
    sim_sum_2[time_step, 2] <- sim_new$basic_output$resource_results[1];
    sim_sum_2[time_step, 3] <- sim_new$basic_output$observation_results[1];
    sim_sum_2[time_step, 4] <- sim_new$basic_output$manager_results[3];
    sim_sum_2[time_step, 5] <- sum(sim_new$basic_output$user_results[,3]);
    sim_old                 <- sim_new;
}
colnames(sim_sum_2) <- c("Time", "Pop_size", "Pop_est", "Cull_cost", 
                         "Cull_count");
print(sim_sum_2);
```
